Staged Abstract Interpreters

### 2019-02-20 paper/21_bg_interp.tex
misc

\begin{lstlisting}
abstract class Expr
case class Lit(i: Int)                         // numbers
case class Var(x: String)                      // variables
case class Lam(x: String, e: Expr)             // lambda abstractions
case class App(e1: Expr, e2: Expr)             // applications
case class AOp(op: String, e1: Expr, e2: Expr) // primitive operations
case class Rec(x: String, rhs: Expr, e: Expr)  // recursive bindings
case class If0(e1: Expr, e2: Expr, e3: Expr)   // conditionals
\end{lstlisting}

>>>>

\begin{lstlisting}
abstract class Expr
case class Lit(i: Int) extends Expr                         // numbers
case class Var(x: String) extends Expr                      // variables
case class Lam(x: String, e: Expr) extends Expr             // abstractions
case class App(e1: Expr, e2: Expr) extends Expr             // applications
case class If0(e1: Expr, e2: Expr, e3: Expr) extends Expr   // conditionals
case class Rec(x: String, rhs: Expr, e: Expr) extends Expr  // recursions
case class AOp(op: String, e1: Expr, e2: Expr) extends Expr // primitives
\end{lstlisting}
